---
title: "R Notebook"
output: html_notebook
---

```{r, message=FALSE, warning=FALSE}
library(tidyverse)
```

```{r}
st <- storms

head(st)
summary(st)
```

Getting the number of storms recorded and how many of each status type there are.
```{r}
st$name %>%
    unique() %>%
    length()

count(st, status)
```

This is which storms turn into a hurricane. I'm not sure how to do this with 1 pipe, so I just used 2. 
```{r}
hu <- st %>%
    filter(status == 'hurricane')

hu_names <- hu$name %>% 
    unique()
cat('There are:', length(hu_names), 'hurricanes.')
```


```{r}
ggplot(st, aes(lat, long, color=status)) +
    geom_point()
```

```{r}
ggplot(st, aes(lat, long, color = year)) +
    geom_line()
```


```{r}
cw <- ChickWeight

cw <- as.tibble(cw) %>%
    rename(Weight = weight)
```

Question: Find the number of Chick in each Diet
```{r}
#Count by itself does not work because each Chick has multiple rows. Instead we must filter out the 
count(cw, Diet)

a <- cw %>%
    select(Chick, Diet)

b <- a[!duplicated(a$Chick),]

count(b, Diet)
```
More concise way of doing it.
```{r}
t <- cw %>% distinct(Chick, Diet) %>% count(Diet)
t

```


```{r}
ggplot(cw, aes(Time, Weight, color=Diet)) +
    geom_point()
```

```{r}
ggplot(cw, aes(Diet, Weight)) +
    geom_boxplot() +
    geom_jitter(aes(color=Diet), width=0.5)
```

```{r}
ggplot(cw, aes(Weight, fill=Diet)) +
    geom_histogram(position='stack', binwidth=20)
```

```{r}
ggplot(cw, aes(Weight, fill=Diet)) +
    geom_density(alpha=0.40)
```


Stuff to do. 
1) Create a linear model for each of the diets.
2) Run ANOVA on each of them
3) Find visualizes I can create based on time.




















